### 2012-07-30 inst/examples/logistic_uniform.Rmd

`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="logistic_uniform_c0/", verbose=TRUE or`

@@

``` {r  profit}
price <- 1
c0 <- 0.01
c1 <- 0
profit <- profit_harvest(price=price, c0 = c0, c1=c1) 
````

@@

  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=2e4)
  opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                       profit, delta, reward=0)
}
````

>>>>

`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="logistic_uniform_c01/", verbose=TRUE or`

@@

``` {r  profit}
price <- 1
c0 <- 0.1
c1 <- 0
profit <- profit_harvest(price=price, c0 = c0, c1=c1) 
````

@@

  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=1e4)
  opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                       profit, delta, reward=0)
}
````
